Should I AirBNB My Property?

### 2017-01-25 abbReturns_Script.Rmd
Addin working analysis to script

  source(paste0(code.path, "dataviztools/ggplottools.R"))
  source(paste0(code.path, "datamgmttools/dataMungetools.R"))
  source(paste0(code.path, "research/AirBNBMelbourne/analysis_Functions.R"))
  source(paste0(code.path, "research/AirBNBMelbourne/dataPrep_Functions.R"))

@@

save(before.PT, subs, file="C:/Dropbox/Research/airBNB/data/analyzed/abb_beforePT.RData")

@@

## Cross impute rates and ltrs

### Global

### By submarkets

### Matching for validation

### - Short to Long

### - Long to Short

## Vacancy Models

# Estimate the ltral income for all properties

## Other costs/fees/income considerations

## Overall rate of return calculations and comparisons

### - Rates by Product Type (Bed/Bath)

### - Rates by Location (Suburb)

### - Rates by Proximity (Near train stations / beach / event grounds, etc.)

>>>>

  source(paste0(code.path, "dataviztools/ggplottools.R"))
  source(paste0(code.path, "datamgmttools/dataMungetools.R"))
  source(paste0(code.path, "research/AirBNBMelbourne/analysis_Functions.R"))
  source(paste0(code.path, "research/AirBNBMelbourne/dataPrep_Functions.R"))
  source("c:/code/spatialtools/point2surface_Tools.R")
  source("c:/code/spatialtools/spatiallogitmodels.R")

@@

#save(before.PT, subs, file="C:/Dropbox/Research/airBNB/data/analyzed/abb_beforePT.RData")

@@

## Global Market Analysis

We now analyze the full metro market to test which properties are more profitable as short-term rentals.

We start by specifying the imputation models for the LTR and the Airbnb datasets

  ltr.mod.spec <- formula(log(event.price) ~ as.factor(type) + 
                            as.factor(bedbath) + as.factor(suburb) + 
                            as.factor(ltr.month))
  abb.mod.spec <- formula(log(nightly.rate) ~ as.factor(type) + 
                            as.factor(bedbath) + as.factor(suburb))

We then employ a custom function to cross impute rates and rents for the two datasets.  The 'clip.field' is a spatial fixed effects that add spatial recognition to the models.

  imp.data <- imputeRatesRents(ltr.df=ltr.data, 
                               abb.df=abb.data, 
                               ltr.mod.spec=ltr.mod.spec, 
                               abb.mod.spec=abb.mod.spec,
                               clip.field='suburb')

From the imputed results, we extract the base data (with imputed values) as well as the model summaries.

  # Extract out DFs (only those that imputed)
  abb.imp <- imp.data$abb
  ltr.imp <- imp.data$ltr

  # Extract models
  abb.sum <- summary(imp.data$abb.mod)
  ltr.sum <- summary(imp.data$ltr.mod)

We use the base data to impute the likely annual revenue for each tenure type (within tenure). These estimates are added back to the base data.

  imp.revs <- revenueEngine(abb.imp, 
                            ltr.imp,
                            rate.field='imp.rate',
                            rent.field='imp.rent')

  abb.imp$imp.revenue <- imp.revs$abb
  ltr.imp$imp.revenue <- imp.revs$ltr

Next we cross impute days on market and occupancy rates.

  # Apply dom to abb
  abb.imp$imp.dom <- imputeDOM(abb.imp, ltr.imp, calc.type='median')

  # Apply occ.rate to ltr
  ltr.imp$imp.occ <- imputeOccRate(ltr.imp, abb.imp, calc.type='median')

With the cross-imputed DOMs and occupancy rates we now make the cross-tenure imputations of revenues and add them back to the original datasets.

  impx.revs <- revenueEngine(abb.df=ltr.imp, 
                             ltr.df=abb.imp,
                             rate.field='imp.rate',
                             rent.field='imp.rent',
                             occ.field='imp.occ',
                             dom.field='imp.dom')

  abb.imp$imp.ltr.revenue <- impx.revs$ltr
  ltr.imp$imp.abb.revenue <- impx.revs$abb

Next, we compare the revenues from the two and extract the new datasets.

  comp.revs <- compareRevenues(abb.imp, ltr.imp)

  abb.revs <- comp.revs$abb
  ltr.revs <- comp.revs$ltr

### Analyze Results

First we make a comparison table of the results, broken down by submarket.

  mrkt.table <- createCompTable(abb.revs, ltr.revs, 'sub.mrkt')
  mrkt.table$ID <- factor(mrkt.table$ID, 
                          levels=c('city-core', 'city', 'suburban', 'rural', 'beach'))

We plot these results in a 2x2 matrix to show the preference likelihoods under the 4 possible scenarios.

 twotwo.bar.plot <- 
    ggplot(mrkt.table, 
                            aes(x=ID, weights=Var, fill=ID)) + 
    geom_bar() +
    facet_grid(est ~ data) +
    scale_fill_manual(values=sm.col) +
    xlab('') +
    ylab('% of properties where Airbnb is more profitable') +
    scale_y_continuous(breaks=c(0,.25,.5,.75,1),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='none')

We find the results from the four highly variable.  Much of this is due to the unreliability of the occupancy and nightly rate estimates for the LTR data.  We build a set of diagrams and charts to explain the differences.

First, we build out the information for each diagram

 mrkt.table$est[c(1:5, 11:15)] <- 'Imp. Rates & Rents'
  mrkt.table$x <- 0
  mrkt.table$y <- 0
  mrkt.table$good <- c(rep('bad', 5), rep('good', 5), rep('bad', 10))

  blank.plot <- ggplot(mrkt.table, 
         aes(x=x, y=y)) +
    facet_grid(est ~ data) +
    scale_fill_manual(values=c('salmon', 'lightgreen')) +
    theme(legend.position='none',
          axis.line=element_blank(),
          axis.text.x=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.grid.minor = element_blank(),
          panel.grid.major = element_blank())

  ann.df <- data.frame(x=rep(0, 4),
                      y=rep(0, 4), 
                      lab=c(paste0('Airbnb Properties: \n (Actual Airbnb Revenue \n vs.',
                                   '\n Imputed Long Term Revenue)'),
                            paste0('Long-Term Properties: \n (Imputed Airbnb Revenue \n vs.',
                                   '\n Actual Long Term Revenue)'),
                            paste0('Airbnb Properties: \n (Imputed Airbnb Revenue \n vs.',
                                   '\n Imputed Long Term Revenue)'),
                            paste0('Long-Term Properties: \n (Imputed Airbnb Revenue \n vs.',
                                   '\n Imputed Long Term Revenue)')),
                      est=c('Actual Rates & Rents', 'Actual Rates & Rents',
                            'Imp. Rates & Rents', 'Imp. Rates & Rents'),
                      data=c('Airbnb', 'Long-Term', 'Airbnb', 'Long-Term'))

  reason.df <- data.frame(x=rep(0, 4),
                       y=rep(0, 4), 
                       lab=c(paste0('+ Actual occupancy rates \n',
                                    '+ Actual nightly rates'),
                             paste0('- Imputed occupancy rates \n',
                                    '- Imputed nightly rate estimates'),
                             paste0('+ Actual occupancy rates \n', 
                                    '- Imputed nightly rate estimates'),
                             paste0('- Imputed occupancy rates \n',
                                    '- Imputed nightly rate estimates')),
                       est=c('Actual Rates & Rents', 'Actual Rates & Rents',
                             'Imp. Rates & Rents', 'Imp. Rates & Rents'),
                       data=c('Airbnb', 'Long-Term', 'Airbnb', 'Long-Term'))

  num.df <- data.frame(x=rep(0, 4),
                       y=rep(.8, 4),
                       est=as.factor(c('Actual Rates & Rents', 'Imp. Rates & Rents',
                             'Actual Rates & Rents', 'Imp. Rates & Rents')),
                       data=as.factor(c('Airbnb', 'Airbnb', 'Long-Term', 'Long-Term')),
                       count=c(1,3,2,4))

We then construct a plot explaining the data/imputations involved

  explain.plot <- blank.plot +
    geom_text(data=ann.df,
              label=ann.df$lab,
              size=3) +
    geom_text(data=num.df,
              label=num.df$count,
              size=9.5) +
    coord_cartesian(ylim=c(-.5,1))

And then a plot that gives the reasons for selecting only the upper left scenario.

  reason.plot <- blank.plot +
    geom_rect(data = mrkt.table, aes(fill=good),
              xmin = -Inf,xmax = Inf,
              ymin = -Inf,ymax = Inf, alpha = 0.4) +
    geom_text(data=reason.df,
              label=reason.df$lab,
              size=3) +
    geom_text(data=num.df,
              label=num.df$count,
              size=9.5) +
    coord_cartesian(ylim=c(-.5,1))

From the upper left we make a simpler table and plot the preferences by submarket.

  abb.act.table <- mrkt.table[mrkt.table$est == 'Actual Rates & Rents' &
                               mrkt.table$data == 'Airbnb', ]

  abb.act.plot <- 
    ggplot(abb.act.table, 
           aes(x=ID, weights=Var, fill=ID)) + 
    geom_bar() +
    scale_fill_manual(values=sm.col) +
    xlab('') +
    ylab('% of properties where Airbnb is more profitable') +
    scale_y_continuous(breaks=c(0,.25,.5,.75,1),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='none') +
    coord_cartesian(ylim=c(0,1))

Next, we plot the \% of properties that have short-term preference versus the occupancy rate

  rawocc.pplot <- makePrefPlot(abb.revs,
                               x.field='occ.rate',
                               y.field='abb.act',
                               group.field='sub.mrkt',
                               smooth=TRUE,
                               smooth.span=.75)
  rawocc.pplot <- rawocc.pplot +
    xlab('\nOccupancy Rate') +
    ylab('\n% of Properties where Airbnb is more profitable') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    scale_color_manual(values=sm.col)

Looking at the distribution of occupancy rates, we that it is not uniform in any of the submarkets.

  abb.revs$sub.mrkt <- factor(abb.revs$sub.mrkt, 
                         levels=c('city-core', 'city', 'suburban', 'rural', 'beach'))
  ggplot(abb.revs, aes(x=occ.rate, group=sub.mrkt, color=sub.mrkt, fill=sub.mrkt)) +
    geom_density(alpha=.3) +
    facet_wrap(~sub.mrkt) +
    scale_color_manual(values=sm.col) +
    scale_fill_manual(values=sm.col) +
    scale_x_continuous(breaks=seq(0, 1, by=.5),
                       labels=c('0%', '50%', '100%')) +
    ylab('') +
    xlab('Occupancy Rate') +
    theme(legend.position='none',
          axis.line=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks=element_blank(),
          axis.title.y=element_blank())

We then calculate quantile values for rates and replot the charts

  abb.revs$occ.qtl <- makeWtdQtl(abb.revs$occ.rate, 
                                      return.type='rank') 
  abb.revs$rate.qtl <- makeWtdQtl(abb.revs$med.rate, 
                                  return.type='rank')

  ## Make quartile location plot

  qtlocc.pplot <- makePrefPlot(abb.revs,
                               x.field='occ.qtl',
                               y.field='abb.act',
                               group.field='sub.mrkt',
                               smooth=TRUE,
                               smooth.span=.75)
  qtlocc.pplot <- qtlocc.pplot +
    xlab('\nQualtile of Occupancy Rate') +
    ylab('\n% of Properties where Airbnb is more profitable') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0', '25th', '50th', '75th', '100th')) +
    scale_y_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    scale_color_manual(values=sm.col)

Next we build a heat map that shows which combinations of occ rate and nightly rate are most likely to result in short-term preference.

  rate.hm <- makeHeatMap(abb.revs,
                x.field='occ.rate',
                y.field='nightly.rate',
                color.field='abb.act',
                bins=c(.05, 25),
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))

  rate.hm <- rate.hm +
    xlab('\n Occupancy Rate') +
    ylab('\n Nightly Rate') +
    scale_x_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='bottom')

To make the distinction more clear, we employ a Support Vector Machine to classify the areas into short and long term preference.

  rate.hm.svm <- makeHeatMap(abb.revs,
                         x.field='occ.rate',
                         y.field='nightly.rate',
                         color.field='abb.act',
                         bins=c(.05, 25),
                         svm=T, 
                         alpha.count=F,
                         add.points=T,
                         fill.colors=c(abb.col[1], abb.col[5]))

  rate.hm.svm <- rate.hm.svm +
    xlab('\n Occupancy Rate') +
    ylab('\n Nightly Rate') +
    scale_x_continuous(breaks=seq(0, 1, by=.25),
                       labels=c('0%', '25%', '50%', '75%', '100%')) +
    theme(legend.position='bottom')

Again, due to the non-uniformity of distribution of these two axis, we convert to quantiles and re-plot.

  qtl.hm <- makeHeatMap(abb.revs,
                         x.field='occ.qtl',
                         y.field='rate.qtl',
                         color.field='abb.act',
                         bins=c(5, 5),
                         svm=F, 
                         alpha.count=T,
                         add.points=T,
                         fill.colors=c(abb.col[1], abb.col[5]))

  qtl.hm <- qtl.hm +
    xlab('\n Quantile of Occupancy Rate') +
    ylab('\n Quantile of Nightly Rate') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0', '25th', '50th', '75th', '100th')) +
    scale_y_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0', '25th', '50th', '75th', '100th')) +
    theme(legend.position='bottom')

  qtl.hm.svm <- makeHeatMap(abb.revs,
                        x.field='occ.qtl',
                        y.field='rate.qtl',
                        color.field='abb.act',
                        bins=c(5, 5),
                        svm=T, 
                        alpha.count=F,
                        add.points=T,
                        fill.colors=c(abb.col[1], abb.col[5]))

  qtl.hm.svm <- qtl.hm.svm +
    xlab('\n Quantile of Occupancy Rate') +
    ylab('\n Quantile of Nightly Rate') +
    scale_x_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0', '25th', '50th', '75th', '100th')) +
    scale_y_continuous(breaks=seq(0, 100, by=25),
                       labels=c('0', '25th', '50th', '75th', '100th')) +
    theme(legend.position='bottom')

Finally, we calculate the areas of the heat maps and combine into a table.

  svm.rate <- makeSVM(abb.revs,
                     x.field='occ.rate',
                     y.field='nightly.rate',
                     z.field='abb.act',
                     svm.type='C-svc',
                     svm.kernel='polydot',
                     poly.degree=4,
                     expand.factor=100)

  svm.qtl <- makeSVM(abb.revs,
                      x.field='occ.qtl',
                      y.field='rate.qtl',
                      z.field='abb.act',
                      svm.type='C-svc',
                      svm.kernel='polydot',
                      poly.degree=4,
                      expand.factor=100)

  market.ratio <- data.frame(type=c('rate', 'qtl'),
                             actual=rep(mean(abb.revs$abb.act), 2),
                             fitted=c(mean(svm.rate$orig$fitted),
                                      mean(svm.qtl$orig$fitted)),
                             svm=c(mean(svm.rate$pred$pred),
                                   mean(svm.qtl$pred$pred)))
```

### Submarkets

We now take the analytical process just completed on the entire metro and apply it to various submarkets.  We use a custom function that combines all the processes above into a single command.

#### Property Type

We start by comparing apartments to houses.  First we set a new imputation model specification

  # Set model specifications
  ltr.mod.spec <- formula(log(event.price) ~ as.factor(bedbath) + as.factor(suburb) + 
                            as.factor(ltr.month))
  abb.mod.spec <- formula(log(nightly.rate) ~ as.factor(bedbath) + as.factor(suburb))

We then recompute the market analysis for each property type.

  # Select data
  abb.apt <- which(abb.revs$type == 'Apartment')
  ltr.apt <- which(ltr.revs$type == 'Apartment')

  # Estimate House Results  
  house <- fullMarketAnalysis(ltr.df=ltr.revs[-ltr.apt,],
                              abb.df=abb.revs[-abb.apt, ],
                              ltr.mod.spec=ltr.mod.spec,
                              abb.mod.spec=abb.mod.spec,
                              clip.field='suburb',
                              market.field='none',
                              mrkt.col=sm.col,
                              heat.col=c(abb.col[1], abb.col[5]))

   apt <- fullMarketAnalysis(ltr.df=ltr.revs[ltr.apt,],
                             abb.df=abb.revs[abb.apt, ],
                             ltr.mod.spec=ltr.mod.spec,
                             abb.mod.spec=abb.mod.spec,
                             clip.field='suburb',
                             market.field='sub.mrkt',
                             mrkt.col=sm.col,
                             heat.col=c(abb.col[1], abb.col[5]))

Below are the quantile heat maps showing the differences in results

ggMultiPlots(house$qtl.hm.svm, apt$qtl.hm.svm, cols=2)

#### Geographic Submarkets

We now do the same for geographic submarkets

# Set model specifications
  ltr.mod.spec <- formula(log(event.price) ~ as.factor(type) + 
                          as.factor(bedbath) +
                          as.factor(suburb) + 
                          as.factor(ltr.month))
  abb.mod.spec <- formula(log(nightly.rate) ~ as.factor(type) + 
                          as.factor(bedbath) +
                          as.factor(suburb))

  #  Extract levels and set capture
  s.levels <- levels(abb.revs$sub.mrkt)
  sm.results <- list()
  sm.pos <- 1

  # Estimate results
  for(sm in s.levels){

    abb.x <- which(abb.revs$sub.mrkt == sm)
    ltr.x <- which(ltr.revs$sub.mrkt == sm)

    x.res <- fullMarketAnalysis(ltr.df=ltr.revs[ltr.x,],
                                abb.df=abb.revs[abb.x, ],
                                ltr.mod.spec=ltr.mod.spec,
                                abb.mod.spec=abb.mod.spec,
                                clip.field='suburb',
                                market.field='sub.mrkt',
                                mrkt.col=sm.col,
                                heat.col=c(abb.col[1], abb.col[5]))

    sm.results[[sm.pos]] <- x.res
    sm.pos <- sm.pos + 1

  }
  names(sm.results) <- as.character(s.levels)

And for bed/bath combinations

  # Set model specifications
  ltr.mod.spec <- formula(log(event.price) ~ as.factor(type) + 
                            as.factor(suburb) + 
                            as.factor(ltr.month))
  abb.mod.spec <- formula(log(nightly.rate) ~ as.factor(type) + 
                            as.factor(suburb))

  # Set levels and capture
  bb.levels <- levels(abb.revs$bedbath)
  bb.results <- list()
  bb.pos <- 1

  # Estimate results
  for(bb in bb.levels){

    abb.x <- which(abb.revs$bedbath == bb)
    ltr.x <- which(ltr.revs$bedbath == bb)

    x.res <- fullMarketAnalysis(ltr.df=ltr.revs[ltr.x,],
                                abb.df=abb.revs[abb.x, ],
                                ltr.mod.spec=ltr.mod.spec,
                                abb.mod.spec=abb.mod.spec,
                                clip.field='suburb',
                                market.field='bedbath',
                                mrkt.col=sm.col,
                                heat.col=c(abb.col[1], abb.col[5]))

    bb.results[[bb.pos]] <- x.res
    bb.pos <- bb.pos + 1

  }
  names(bb.results) <- as.character(bb.levels)

And by geo submarket and property type combined

  # Set model specifications
  ltr.mod.spec <- formula(log(event.price) ~ as.factor(suburb) + 
                            as.factor(ltr.month))
  abb.mod.spec <- formula(log(nightly.rate) ~ as.factor(suburb))

  # Create smt variable  
  abb.revs$smt <- as.factor(paste0(abb.revs$type, '.', abb.revs$sub.mrkt))
  ltr.revs$smt <- as.factor(paste0(ltr.revs$type, '.', ltr.revs$sub.mrkt))

  # Create levels and captures
  smt.levels <- levels(abb.revs$smt)
  smt.results <- list()
  smt.pos <- 1

  # Estimate the smt models
  for(smt in smt.levels){

    abb.x <- which(abb.revs$smt == smt)
    ltr.x <- which(ltr.revs$smt == smt)

    x.res <- fullMarketAnalysis(ltr.df=ltr.revs[ltr.x,],
                                abb.df=abb.revs[abb.x, ],
                                ltr.mod.spec=ltr.mod.spec,
                                abb.mod.spec=abb.mod.spec,
                                clip.field='suburb',
                                market.field='smt',
                                mrkt.col=sm.col,
                                heat.col=c(abb.col[1], abb.col[5]))

    smt.results[[smt.pos]] <- x.res
    smt.pos <- smt.pos + 1
  }
  names(smt.results) <- as.character(smt.levels)

### Further analysis

The above present, essentially, univariate analyses of each of the submarkets in question.  While illustrative, they do not hold constant other differences in co-variates that might affect short term preference.  To better control for these influences we estimate a set of logistic regression model to estimate the impact of various variables on short-term preference.

Before we begin, we do a bit of data preparation: extracting abb data and fixing the cancellation policy variable.

  smt.data <- rbind.fill(lapply(smt.results, function(x) x$abb))

  ss60 <- which(smt.data$cancel.policy == 'Super Strict 60 Days')
  smt.data$cancel.policy[ss60] <- 'Strict'
  cpmiss <- which(smt.data$cancel.policy == '')
  smt.data <- smt.data[-cpmiss, ]

First, we look only at structural characteristics.

  mod.str <- glm(abb.act~type+as.factor(bedbath),
                 family=binomial(link='logit'),
                 data=smt.data)

We then add geographic submarkets.

   mod.sm <- glm(abb.act~type+as.factor(bedbath)+
                  sub.mrkt,
                 family=binomial(link='logit'),
                 data=smt.data)

And, finally, host policy actions.

   mod.host <- glm(abb.act~type+as.factor(bedbath)+
                    sub.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                  family=binomial(link='logit'),
                  data=smt.data)

We add suburb fixed effects and re-estimate the str and host models.

  # Suburb model
  mod.sub <- glm(abb.act~type+as.factor(bedbath)+
                   suburb,
                 family=binomial(link='logit'),
                 data=smt.data)

  # Suburb Host model
  mod.subh <- glm(abb.act~type+as.factor(bedbath)+
                  suburb+
                  max.guests+min.stay+
                  I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                  family=binomial(link='logit'),
                  data=smt.data)

We then extract the coefficients and diagnostics and build a table for viewing purposes.

 ## Extract Coef

  str.ct <- summary(mod.str)$coef
  sm.ct <- summary(mod.sm)$coef
  host.ct <- summary(mod.host)$coef

  # Assign SS
  f.l <- nrow(host.ct)
  assignSS <- function(x){

    y<-rep('   ', length(x))
    y[x<.1] <- '*  '
    y[x<.05] <- '** '
    y[x<.01] <- '***'

    y
  }

  # Build coefs with SS
  str.coef <- sprintf("%.3f" ,str.ct[,1])
  str.sig <- assignSS(str.ct[,4])
  str.coef <- c(paste0(str.coef, str.sig), rep(' ', f.l - nrow(str.ct)))

  sm.coef <- sprintf("%.3f" ,sm.ct[,1])
  sm.sig <- assignSS(sm.ct[,4])
  sm.coef <- c(paste0(sm.coef, sm.sig), rep(' ', f.l - nrow(sm.ct)))

  host.coef <- sprintf("%.3f" ,host.ct[,1])
  host.sig <- assignSS(host.ct[,4])
  host.coef <- c(paste0(host.coef, host.sig), rep(' ', f.l - nrow(host.ct)))

  # Combine into table
  mod.table <- data.frame(Variable=rownames(host.ct),
                          Str.Model=str.coef,
                          Sm.Model=sm.coef,
                          Host.Model=host.coef)

  # Fix variable names
  mod.table$Variable <- c('Intercept', 'House', '1Bed/1Bath','2Bed/1Bath',
                          '3Bed/1Bath', '3Bed/2Bath', '4Bed/2Bath', 'City',
                          'Suburban','Rural', 'Beach', 'Guests/Bedroom',
                          'Min. Stay', 'Flexible Cancel', 'Strict Cancel')

 ## Create model diagnostics

  # Custom function
  logDx <- function(log.model, data, resp.var){

    pred <- prediction(predict(log.model, data, type='response'), resp.var)
    auc <- performance(pred, measure='auc')
    ll <- logLik(log.model)
    AIC <- AIC(log.model)

    return(list(AIC=AIC,
                logLik=ll,
                auc=auc))
  }

  # Extract diagnostics
  str.dx <- logDx(mod.str, smt.data, smt.data$abb.act)
  sm.dx <- logDx(mod.sm, smt.data, smt.data$abb.act)
  host.dx <- logDx(mod.host, smt.data, smt.data$abb.act)

  # Create diagnostic table
  diag.table <- data.frame(Variable=c('', 'Diagnostics', 'AIC', 'LogLik', 'AUC'),
                           Str.Model=c('', '', round(str.dx$AIC,0), 
                                       round(str.dx$logLik, 0),
                                       round(as.numeric(str.dx$auc@y.values), 3)),
                           Sm.Model=c('', '', round(sm.dx$AIC,0), 
                                      round(sm.dx$logLik, 0),
                                      round(as.numeric(sm.dx$auc@y.values), 3)),
                           Host.Model=c('', '', round(host.dx$AIC,0), 
                                        round(host.dx$logLik, 0),
                                        round(as.numeric(host.dx$auc@y.values), 3)))

 ## Combine into full table of coef and diags

 full.table <- rbind(mod.table, diag.table)

### Moving Window Logit

To better capture the spatial variation in the logit model results, we set up a moving window logit model that estimates a different model at each estimation point on the map.  Before beginning, we import a new suburbs shapefile and trim it to those suburbs with Airbnb properties. 
```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 ssubs <- table(abb.revs$suburb)
 s.subs <- subs[subs$id %in% names(ssubs),]
 s.suburbs <- suburbs.shp[suburbs.shp@data$NAME_2006 %in% names(ssubs),]
 sssubs <- fortify(s.suburbs)

Next we set up the prediction points.  We drap a grid over the entire area and use those points for prediction points.

 # Min, Max and Range
 xmin <- min(s.subs$long)
 xmax <- max(s.subs$long)
 ymin <- min(s.subs$lat)
 ymax <- max(s.subs$lat)
 xrange <- xmax-xmin
 yrange <- ymax-ymin

 # Set Scale
 scale <- mean(xrange, yrange)/100

 # Create estimation points
 est.data <- abb.revs
 est.points <- createGridPoints(s.suburbs, scale, T)

We then specify the logistic regression model and set the moving window bandwidth.

 ## Set model specification

 mod.spec <- abb.act ~ type + as.factor(bedbath) + 
   I(max.guests / bedrooms) + min.stay + 
   I(cancel.policy == 'Flexible') + 
   I(cancel.policy == 'Strict')

 ## Set bandwidth

 k <- 400

The results are estimated with the custom MWL function

 mwl.results <- mwl(est.data, 
                    est.points, 
                    mod.spec, 
                    k)

Coefficents are extracted and put into a data.frame

# Extract coef Names
 coef.names <- rownames(mwl.results[[1]])

 # Create a list to capture
 coef.list <- list()

 # Create a data.frame to capture
 coef.df <- data.frame(lat=est.points@coords[,2],
                       long=est.points@coords[,1])

 # Loop through and extract coefficients
 for(cn in 1:length(coef.names)){
   coef.list[[cn]] <- lapply(mwl.results, getMWLCoef, coef=coef.names[cn])
   coef.df[,ncol(coef.df)+1] <- unlist(coef.list[[cn]])
 }

 # Add plottable names
 colnames(coef.df)[3:13] <- c('intercept', 'house', 'bb11', 'bb21', 'bb31',
                              'bb32', 'bb42', 'guest', 'minstay', 'flex', 'strict')

Finally, these coefficients are converted to a surface.

 # Make capture list
 surf.list <- list()

 # Create surfaces
 for(sl in 1:ncol(coef.df)){

   # If NAs
   to.cut <- which(is.na(coef.df[,sl]))
   if(length(to.cut) > 0){
     surf.points <- est.points[-to.cut,]
     surf.value <- coef.df[-to.cut, sl]
   } else {
     surf.points <- est.points
     surf.value <- coef.df[ , sl]
   }

   # Surface estimation
   surf.list[[sl]] <- point2Surface(surf.points, 
                                    surf.value,
                                    .01, 
                                    1.5)
 }

```{r working, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

### Save workspace -----------------------------------------------------------------------

  save.image("C:/Dropbox/Research/airBNB/data/analyzed/abb_results.RData")

  save(abb.revs, ltr.revs, clean.count, blank.plot,
       rate.hm, rate.hm.svm, qtl.hm, qtl.hm.svm, market.ratio, 
       house, apt, sm.results, full.table, smt.results, bb.results,
       abb.sum, ltr.sum, ann.df, mrkt.table, num.df, reason.df, subs,
       suburbs.shp, s.suburbs, coef.df,
       file="C:/Dropbox/Research/airBNB/data/analyzed/abb_objs.RData")
